---
title: "git_try"
author: "Nilanjan"
date: "20 October 2019"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Species Cooccurrence

There are several exisitng ways to calculate the cooccuurence of species from sampling sites. Veech et al. 2014 came up with a R package "cooccur" to calculate the species cooccurrence and test the cooccurrence with several random distribution of species in those sites.

These cooccurrence package provides a vector but that is not enough to plot species cooccurrence network as those are lower triangular and lacks the diagonal element and non-significant species interactions.
```{r}
library(cooccur)
library(igraph)
```

## Load your data

You need sites x species matrix to calculate the cooccurrence matrix

```{r}
getwd()
setwd("D:/Work/River bird")
try3 <-read.csv("ecos_2014_spr_aut.csv",header = T)
head(try3)
```

## Calculate species cooccurrence based on Veech et al. 2014
The dataset I loaded has both summer and autumn data, I am subsetting the data into two parts for easier understanding
```{r, results='hide'}
try31 <-try3[1:40, 2:17]
try32 <-try3[41:80, 2:17]
cooc_sum <-cooccur(t(try31), spp_names = T)
cooc_aut <-cooccur(t(try32), spp_names = T)
```

## Plotting the cooccurrence 
```{r}
par(mfrow=c(2,1))
plot(cooc_sum)
plot(cooc_aut)
```

## Calculate species cooccurrence based on my methodology
The cluster sequences of the birds used to make two clusters in the plot, are obtained from Grade of Membership Model (Wild et al. 2019)
Cooccurrence for summer season
```{r}
cormat<-matrix(data = NA, nrow=16, ncol=16)
for(i in 1:16)
{
  for(j in 1:16)
  {
    cormat[i,j]<-sum(as.numeric(try31[,i]>0)*as.numeric(try31[,j]>0))/(sum(as.numeric(try31[,i]>0))+sum(as.numeric(try31[,j]>0)))
  }
}
network <- graph_from_adjacency_matrix(cormat, weighted=T, mode="undirected", diag=F)

colrs <- c("gray50", "tomato")
clstr <-c("1","1","1","2","1","1","2","2","2","1","1","1","1","2","2","1")
my_color <- colrs[as.numeric(as.factor(clstr))]

```

Cooccurrence for autumn season
```{r}
cormat1<-matrix(data = NA, nrow=16, ncol=16)
for(i in 1:16)
{
  for(j in 1:16)
  {
    cormat1[i,j]<-sum(as.numeric(try32[,i]>0)*as.numeric(try32[,j]>0))/(sum(as.numeric(try32[,i]>0))+sum(as.numeric(try32[,j]>0)))
  }
}
network1 <- graph_from_adjacency_matrix(cormat1, weighted=T, mode="undirected", diag=F)

```

## Plotting the cooccurrence network for summer
```{r}
plot(network,edge.arrow.size=.4,vertex.label=colnames(try31), vertex.color=my_color,
     vertex.label.color="black",vertex.label.font=2)
title(main="River bird co-occurrence network in summer", cex=2)
text(1.4,-0.6,"Cluster details",col="black", cex=2.5)
legend(0.2,-0.8,  legend=c("Lowland species","Highland species"), 
       col=colrs,  bty = "n", pch=20 , pt.cex = 5, cex = 1.8,
       text.col="black")
```

## Plotting the cooccurrence network for autumn
```{r}
plot(network1,edge.arrow.size=.4,vertex.label=colnames(try31), vertex.color=my_color,
     vertex.label.color="black",vertex.label.font=2)
title(main="River bird co-occurrence network in autumn", cex=2.5)
text(1.68,-0.66,"Cluster details",col="black", cex=2)
legend(0.9,-0.72,  legend=c("Lowland species","Highland species"), 
       col=colrs,  bty = "n", pch=20 , pt.cex = 5, cex = 1.8,
       text.col="black")
```